NSNEQ_Moon_Example

### 2017-10-18 NSNEQ_Moon_Example.Rmd
minor comments

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Example of effect that is neither significant nor equivalent

@@

1. The data indicate the absence of any effect, and we can accept the null hypothesis.
2. The data are not sensitive enough to tell us whether an effect is present or abscent.

In order to distinguish between these two hypotheses, we calculate the TOST. We first need to define our SESOI (and thus, our bounds). Let us imagine that we consult a teacher about the test, and discover that that grades for this test are set at every 6.25% increase in correct answers (F = 0% to 6.25% ... A+ = 93.75% to 100%). We can decide that we are only interested in test differences so far as they correspond to at least a 1 gradepoint increase or decrease. We can convert this percentage difference into a corresponding Cohen's d for Moon & Roeder's (2014) data by multiplying 6.25/100 on the pooled standard deviation of the groups.

@@

```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!-- I don't think we need to say 'Welch's t-test. We might throw in a quick remakr that by default, the TOST package reports Welch's t-test (following Delacre et al., 2017) -->  
# Example of an effect that is neither statistically significant nor equivalent

@@

1. The data indicate the absence of a meaningful effect, and we can accept the null hypothesis.
2. The data are not sensitive enough to tell us whether a meaningful effect is present or absent.

In order to distinguish between these two hypotheses, we first need to define a SESOI (and thus, our equivalence bounds). Let us imagine that we consult a teacher about the test, and discover that that grades for this test are set at every 6.25% increase in correct answers (F = 0% to 6.25% ... A+ = 93.75% to 100%). We can decide that we are only interested in test differences so far as they correspond to at least a 1 gradepoint increase or decrease. We can convert this percentage difference into a corresponding Cohen's d for Moon & Roeder's (2014) data by multiplying 6.25/100 on the pooled standard deviation of the groups.

@@

```  
<!-- So the TOST results below should not be typed in, but calculated in R, like you do with sesoi.d -->
